Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-05-07 files/Chapter2/generalvibrationmodel.tex
local changes

\subsection{General vibration problem new}
This section is a discussion of a general vibration problem. The discussion will refer to the article \cite{CVV18}. In this article, the authors take damping into consideration, which is not covered in this dissertation. Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.

@@

Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
\begin{flalign}
	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
	T_n(t) &=  A_n \cosh(\sqrt{-\lambda_n} t) + B_n \sinh(\sqrt{-\lambda_n} t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
\end{flalign}

>>>>

\subsection{General vibration problem new}
This section is a discussion of a general vibration problem. The discussion will refer to the article \cite{CVV18}. In this article, the authors take damping into consideration, which is not covered in this dissertation.

Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.

@@

Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
\begin{flalign}
	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}\\
	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda_n = 0, \label{lambda_2}\\
	T_n(t) &=  A_n \cosh(\sqrt{-\lambda_n} t) + B_n \sinh(\sqrt{-\lambda_n} t) \quad \textrm{ if } \lambda_n < 0. \label{lambda_3}
\end{flalign}
